### 2021-02-01 README.Rmd
updated README.Rmd

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Assessment of Northern Pikeminnow Abundance in Deadwater Slough and Potential Impacts to Local Chinook Salmon"
Authors <- "See, Kevin E., Nick Porter, Richard A. Carmichael, and Michael W. Ackerman"
yr <- 2021
Journal <- "TBD"
```

@@

> `r Authors` (`r yr`). _`r Title`_. `r Journal` <https://doi.org/xxx/xxx>

@@

> `r Authors` (`r yr`). _`r Title`_. `r Journal`, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> `r Authors`, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
